Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex

\subsection{Continual learning}

@@

Our experiments seek to answer the following questions:
\begin{enumerate}
  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations? Does our method's ability to consider the full data set offer benefits over subset function-space methods?
  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
  \item \textbf{Function-space updates} How faster are our function-space updates relative to retraining from scratch? Do they improve predictive performance? Are they as good as retraining from scratch?
  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
\end{enumerate}

@@

% \cref{alg-mbrl} shows the typical model-based RL loop.
\begin{align} \label{eq-fast-update-mpc}
  \policy_{i+1}^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
\quad \text{s.t. } \state_{t+1} &= \hat{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
\end{align}
with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$

@@

>>>>

\subsection{Continual Learning}
In Continal Learning,

\begin{equation}
 	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{m \times m}, \quad \forall s \in [1, t-1]
 \end{equation}

\begin{equation}
	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}\left[\left(f_{\vw}(\MZ_{s}) - f_{\vw_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw}(\MZ_{s}) - f_{\vw_{s}}(\MZ_s) \right) \right]
\end{equation} 
with $f_\vw(\MZ_{s}), f_{\vw_s}(\MZ_s) \in \R^m$ are vectors of the outputs of the neural

@@

Our experiments seek to answer the following questions:
\begin{itemize}
  \item Does NN2SFR caputure good uncertainty estimates
  \item Can NN2SFR be used to build a summary of the current neural network to mitigate catastrophic forgetting over previous tasks?
\end{itemize}

@@

% \cref{alg-mbrl} shows the typical model-based RL loop.
\begin{align} \label{eq-fast-update-mpc}
  \policy_{i+1}^{\text{PS}}(\state) = \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
\E \bigg[ \sum_{t=0}^{H-1} \gamma^{t} r(\state_{t},\action_{t}) \mid \state_{0}=\state  \bigg] + Q_{\theta}(\state_{\Horizon}, \action_{H})
\quad \text{s.t. } \state_{t+1} &= \hat{\transitionFn}(\state_{t}, \action_{t}) + \noise_{t}
\end{align}

with $\hat{\transitionFn} \sim p(\transitionFn \mid \dataset)$

@@

\section{Extending the CL regularizer to multi-class settings}
\begin{equation}
	\bar{\MB}^{-1}_s = \MKzz^{-1} \vbeta_\vu \MKzz^{-1} \in \R^{C \times m \times m} \quad \MKzz \in \R^{C \times m \times m} 
\end{equation}

\begin{equation}
	\mathcal{R_\textit{SFR}}(\mathbf{w}) = \sum_{s=1}^{t-1}	\sum_{k \in 	C}\left[\left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s}, k}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\vw, k}(\MZ_{s}) - f_{\vw_{s, k}}(\MZ_s) \right) \right] 
\end{equation}
